---
name: Jaron
surname: Arbet
position: "Senior Bioinformatician"
address: "UCLA Jonsson Comprehensive Cancer Center"
www: jarbet.github.io
email: "jaron.arbet@gmail.com"
#to get the orcid: 0000-0001-6087-0428
googlescholar: hbqQUw0AAAAJ
osf: nrtbk # currently vitae doesn't support osf in the yaml header, need to add \osf{nrtbk} in the .tex file manulaly
github: jarbet
headcolor: 414141 # use black color
date: "`r format(Sys.time(), '%B %Y')`"
csl: apa-cv.csl # change this if you want to use other citation styles
output: 
  vitae::awesomecv:
    keep_tex: true
    pandoc_args: ["--lua-filter=lua/strong.lua"]
header-includes:
  - \usepackage{hyperref}
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae);library(tibble)
library(RefManageR);
#rmarkdown::pandoc_version()
```

# Research Interests

* Machine learning and predictive modeling
* High-dimensional “Big Data”
* Variable selection
* Multi-omics cancer data integration
* Robust nonparametric statistics

# Work Experience

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Notes,
  'April 2022 - Present',
  'Senior Bioinformatician',
  'University of California Los Angeles, CA\\newline \\hspace{1cm} \\newline',
   NULL,

  'Jan 2021 - April 2022',
  'Staff Biostatistician',
  'Edwards Lifesciences, Irvine, CA',
   list(
       'Develop statistical analysis plans and data monitoring for clinical trials',
       'Power and sample size estimation',
       'Clinical study reports for federal regulatory agencies',
       'Perform analyses with large national database (STS/ACC TVT Registry) including propensity score matching for causal inference\\newline \\hspace{1cm} \\newline'
        ),
  
  'Aug 2018 - Jan 2021',
  'Postdoctoral Research Associate',
  'University of Colorado Anschutz Medical Campus, Department of Biostatistics and Informatics, Aurora, CO',
   list(
       'Provided statistical consulting services',
       'Published scientific manuscripts',
       'Developed grants (statistical analysis plan, power/sample size estimation)',
       'Supervised students and MS/MPH degree biostatisticians',
       'Taught BIOS 6601 Intro stats course for 75 MPH students, and created annual 6-week data science machine learning short course',
       'Develop new statistical methodology\\newline \\hspace{1cm} \\newline'
        ),
  
  'June 2014 - July 2018',
  'Research Assitant',
  'University of Minnesota, Division of Biostatistics, Minneapolis, MN',
   list(
       'Developed variable selection methods for high dimensional genetic data and robust methods for estimating the genetic heritability of disease traits\\newline \\hspace{1cm} \\newline'
    ),
  
  'June - Aug 2013',
  'Statistical Genetics Research Intern',
  'Dordt College, Department of Mathematics, Sioux Center, IA ',
   list(
       'Developed methods for aggregating different statistical tests together for greater sensitivity in detecting disease-related genes; resampling-based bias corrected tests\\newline \\hspace{1cm} \\newline'
    ),
  
  'Sept 2012 - May 2014',
  'Math and Statistics Tutor',
  'Winona State University, Winona, MN',
   NULL
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Notes,
    .protect = FALSE
  )
```

# Education

```{r}
tribble(
  ~ Degree,
  ~ Advisor,
  ~ Year,
  ~ Institution,
  ~ Where,
  "PhD Biostatistics",
  "GPA: 3.7\\newline \\hspace{1cm} \\newline",
  "2014-2018",
  "University of Minnesota",
  "Minneapolis, MN, USA",
  
  "B.S. Mathematics and Statistics",
  "GPA: 4.0 | \\textit{Summa Cum Laude}",
  "2010-2014",
  "Wiona State University",
  "Winona, MN, USA"
) %>%
  detailed_entries(
    what = Degree,
    when = Year,
    with = Institution,
    where = Where,
    why = Advisor,
    .protect = FALSE
  )
```

# Awards

## Postdoctoral

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Supp,
  ~ Amount,
  '2023-2024',
  'Staff appreciation and recognition (STAR)',
  'UCLA Jonsson Comprehensive Cancer Center',
   NA,
   NA,
 
  '2022-2023',
  'Staff appreciation and recognition (STAR)',
  'UCLA Jonsson Comprehensive Cancer Center',
   NA,
   NA,
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  )
```


## Student Awards

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Institution,
  ~ Supp,
  ~ Amount,
  '2017-2018',
  'Outstanding Research Assistant Award',
  'University of Minnesota, Division of Biostatistics & Health Data Science',
   NA,
   NA,
 
  '2025-2017',
  'Interdisciplinary Biostatistics Training Grant in Genetics and Genomics',
  'National Institute of General Medical Sciences',
   NA,
   NA,
) %>%
  detailed_entries(
    where = Year,
    with = Name,
    what = Institution,
    why = Supp,
    when = Amount
  ) 
```

## Competitions

```{r}
tribble(
  ~Year, ~Name, ~Institution, ~Supp, ~Amount,
  '2014', 'Midwest Undergraduate Data Analysis Competition (MUDAC)', 'School of Education, University of Michigan', '3\\textsuperscript{rd} place out of 20 teams from 14 universities\\newline \\hspace{1cm} \\newline', NA,
  
  '2014', '1st place in the “predictive-modeling class competition”', 'Winona State University Data Mining Course', NA, NA,
  
  '2013', 'Midwest Undergraduate Data Analysis Competition (MUDAC)', 'School of Education, University of Michigan', '2\\textsuperscript{nd} place out of 15 teams from 10 universities\\newline \\hspace{1cm} \\newline', NA,
) %>% 
  detailed_entries(
    where = Year,
    with = Name, 
    what = Institution,
    why = Supp,
    when = Amount,
    .protect = FALSE
  ) 
```

# Journal Articles

```{r}
bibliography_entries("jaron_published.bib")
```



# Selected Presentations

## Departmental
```{r}
bibliography_entries("Presentations_departmental.bib")
```

## Conferences

```{r}
bibliography_entries("Presentations_conferences.bib")
```

# Teaching Experience

## Semester courses

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  ~ Desc,
  'Fall 2019',
  "BIOS 6601 – Applied Biostatistics I",
  "University of Colorado Anschutz Medical Campus",
  list(
       "\\textbf{\\textit{Duty}}: Sole Instructor, completely redesigned all lectures, homework, quizzes, and exams",
       "\\textbf{\\textit{Description}}: Applied biostatistical methods including descriptive and statistical inference; odds ratio and relative risk, probability theory, parameter estimation, tests for comparing statistics of two or more groups, correlation, linear regression, logistic regression and survival analysis.",
    "\\textbf{\\textit{Credits}}: 3",
    "\\textbf{\\textit{Audience}}: 75 Masters of Public Health (MPH) students\\newline \\hspace{1cm} \\newline"
    )
) %>%
  detailed_entries(
      where = Year,
      with = Name,
      what = Duty,
      why = Desc,
      .protect = FALSE
      )
```

## Short courses

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  ~ Desc,
  'Summer 2019, Fall 2020',
  "Fundamentals of Data Science Literacy",
  "University of Colorado Anschutz Medical Campus",
  list(
       "\\textbf{\\textit{Duty}}: lead organizer, developed and taught 3 machine learning lectures",
       "\\textbf{\\textit{Description}}:6-week short course (2 hours/week) on data science with emphasis on how machine learning and data mining are used in biomedical research.  Topics included: 1) Overview of Data Science; 2) Introduction of Machine Learning in Biomedical Research; 3) Clustering and Pattern Finding (unsupervised Machine Learning); 4) Powerful Predictive Models and Variable Selection (supervised Machine Learning); 5) Fundamentals of Data Visualization; 6): Reproducible Research and Team Science",
    "\\textbf{\\textit{Audience}}: ~20 medical researchers, mostly non-statisticians\\newline \\hspace{1cm} \\newline"
    ),
  
  'Summer 2019, 2020',
  "Introduction to Statistics",
  "University of Colorado Anschutz Medical Campus",
  list(
       "\\textbf{\\textit{Duty}}: Instructor, developed and taught lectures on “Introduction to statistics”, study design, and survey design",
       "\\textbf{\\textit{Description}}: Introductory statistics day-long short course for UCHealth nurses",
    "\\textbf{\\textit{Audience}}: ~15 UCHealth Nurses\\newline \\hspace{1cm} \\newline"
    )
) %>%
  detailed_entries(
      where = Year,
      with = Name,
      what = Duty,
      why = Desc,
      .protect = FALSE
      )
```

## Guest Lectures

```{r}
tribble(
  ~ Year,
  ~ Name,
  ~ Duty,
  ~ Desc,
  'Nov 2019, Oct 2020',
  "IPHY 5900 – Data Literacy in Biomedical Research",
  "University of Colorado Boulder",
  list(
       "\\textbf{\\textit{Primary Instructor}}: Dr. Celine Marie Claire D. Vetter, Integrative Physiology",
       "\\textbf{\\textit{Lecture}}:Machine Learning in Biomedical Research\\newline \\hspace{1cm} \\newline"
    ),
  
  'Fall 2018',
  "BIOS 6611 – Biostatistical Methods I",
  "University of Colorado School of Public Health",
  list(
       "\\textbf{\\textit{Primary Instructor}}: Dr. Alex Kaizer",
       "\\textbf{\\textit{Lecture}}: Linear Algebra Review\\newline \\hspace{1cm} \\newline"
    )
) %>%
  detailed_entries(
      where = Year,
      with = Name,
      what = Duty,
      why = Desc,
      .protect = FALSE
      )
```

# Mentoring and supervising

## University of California Los Angeles

### Supervising students for data analysis projects {-}

- Yuxi Song
- Sattwik Banerjee
- Adriana Wiggins

## University of Colorado, Department of Biostatistics and Informatics

### Supervising MPH/MS Statisticians {-}

- Laura Grau (MPH), Nov 2018 – Jan 2021
    - I supervised Laura on several projects which led to publications.

### Supervising students for data analysis projects {-}

- Yaxu Zhuang (PhD), Jan 2019 – Aug 2020
- Rachel Weber (MS), Dec 2018 – April 2019

### Thesis or Dissertation Committee Member (graduating year) {-}

- Charlie Carpenter, Biostatistics MS thesis committee, Biostatistics (2020)
- Rachel Blumhagen, Biostatistics PhD dissertation committee (2021)


# Professional Service

## Grant and Protocol Reviews

- Scientific Advisory & Review Committee (SARC), Colorado Clinical and Translational Sciences Institute, University of Colorado – April 2019 to Jan 2021


## Journal Reviewer:

- Biometrics
- Genetic Epidemiology
- PeerJ


## Committees/Other 

### Department of Biostatistics and Informatics, University of Colorado {-}

- Student Admissions Committee, Fall 2018 – Spring 2019
- Volunteer Judge for CIDA Hackathon (24 hour data analysis competition), Jan. 2020

### Biostatistics, Epidemiology, & Research Design Core of the Colorado Clinical and Translational Sciences Institute, University of Colorado {-}

- Education Committee, Fall 2018 – Jan 2020

# Software Skills

## Proficient

**R**

* Over `r as.numeric(format(Sys.Date(), "%Y")) - 2011` years of experience with R for data analysis
* I enjoy developing R packages to easily share documented code with colleagues and the broader research community.  Examples:
    -  https://github.com/arbet003/discoMod
* Parallel programming in R using multiple cpus

**Quarto and Rmarkdown**

* Reproducible research, manuscripts and reports
* Reproducible HTML presentations.  Examples: [https://jarbet.github.io/presentations.html](https://jarbet.github.io/presentations.html)
* Websites: [https://jarbet.github.io/](https://jarbet.github.io/)
* Resume: this resume was made using Rmarkdown with the [vitae R package](https://github.com/mitchelloharawild/vitae)

**Bayesian statistical programming**

* Proficient with BUGS/JAGS; basic skills with STAN


## Basic skills

* Linux command line and bash scripts
* Databricks
* Microsoft Office
* SAS